Conference Paper Title\\

### 2023-06-14 LARS_paper/paper.tex
Add references

The robot's structure is mammal-type, which is characterized by the presence of two joints in the sagittal plane, similar to animals such as dogs and horses.  The robot's legs follow a configuration called full-elbow, in which the four legs are oriented backward, as shown in Fig. X. Furthermore, it features 3 degrees of freedom (DoF) per leg, providing the legs with substantial freedom of movement. The robot was designed to favor the mass balance between the body and the robot's legs, that is, the majority of its mass is located in the body or as close to it as possible. Lighter legs can move quickly without significantly changing the center of gravity of the robot, which increases stability and requires less control complexity.  On the other hand, the legs should be strong enough to support the robot's weight and the impact on the ground.

@@

Quadruped robots move according to a gait pattern. The gait implemented for the robot follows the sequence of phases demonstrated in Fig. \ref{fig:trot_pattern}, in which the white rectangles represent the swing phase and the gray rectangles represent the stance phase. During the stance phase, the legs are on the ground and push the robot in the desired direction.  In the swing phase, the legs are raised and moved to the next support point. This gait pattern is called trot and is based on the concept of periodic and symmetrical gaits. The periodic gaits are characterized by the continuous repetition of the movements in the same instants. Symmetry is a characteristic of gaits that move a pair of legs together, leaving and returning to the ground in a synchronized way. Although the structure of the robot makes it possible to perform other types of gaits, in this work, only the trot was considered. To reduce the control complexity, a discontinuous gait was adopted, that is, the robot's body moves only when all the legs are on the ground, resulting in intermittent movement. In Fig. \ref{fig:trot_pattern}, it is noticeable that the same pair of diagonal legs always move at the same instant. Between two consecutive swing phases, there is a moment when all legs are in the stance phase, which is when the robot body is displaced in the desired direction of locomotion.

@@

The control subsystem of the robot is composed of two main components: the joints' controllers, and the body's stabilization controller. The joints' controllers, each one a PID, are responsible for controlling each joint of the robot independently. Meanwhile, the body's stabilization controller is responsible for controlling the pitch and roll angles of the robot, maintaining it at 0 degrees.

@@

\begin{thebibliography}{00}
  \bibitem{X.134} X. Zhang, L. Lang, J. Wang, and H. Ma, ‘The quadruped robot locomotion based on force control’, Proceedings of the 2015 27th Chinese Control and Decision Conference, CCDC 2015, pp. 5440–5445, 2015.
  \bibitem{ROS2Humble} S. Macenski, T. Foote, B. Gerkey, C. Lalancette, and W. Woodall, ‘Robot Operating System 2: Design, architecture, and uses in the wild’, Science Robotics, vol. 7, no. 66, p. eabm6074, 2022.
  \bibitem{Shi2021} Y. Shi, S. Li, M. Guo, Y. Yang, D. Xia, and X. Luo, ‘Structural design, simulation and experiment of quadruped robot’, Applied Sciences (Switzerland), vol. 11, 2021.
  \bibitem{leotti2005comparaccao} V. B. Leotti, A. R. Birck, and J. Riboldi, ‘Comparação dos Testes de Aderência à Normalidade Kolmogorov-smirnov, Anderson-Darling, Cramer--Von Mises e Shapiro-Wilk por Simulação’, Anais do 11\textordmasculine Simpósio de Estatística Aplicada à Experimentação Agronômica, 2005.
  \bibitem{cano2012six} E. L. Cano, J. M. Moguerza, and A. Redchuk, Six sigma with R: statistical engineering for process improvement, vol. 36. Springer Science \& Business Media, 2012.
  \bibitem{CaramelRepo} B. S. de Alencar, F. M. S. M. Barreto, and L. L. Souza, ‘Caramel’, GitHub repository. 2022.
  % \bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
  % \bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
  % \bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
  % \bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
  % \bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
  % \bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
  % \bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
% \vspace{12pt}
% \color{red}
% IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

>>>>

The robot's structure is mammal-type, which is characterized by the presence of two joints in the sagittal plane, similar to animals such as dogs and horses \cite{Kitano2016}. The robot's legs follow a configuration called full-elbow, in which the four legs are oriented backward, as shown in Fig. X. Furthermore, it features 3 degrees of freedom (DoF) per leg, providing the legs with substantial freedom of movement. The robot was designed to favor the mass balance between the body and the robot's legs, that is, the majority of its mass is located in the body or as close to it as possible. Lighter legs can move quickly without significantly changing the center of gravity of the robot, which increases stability and requires less control complexity. On the other hand, the legs should be strong enough to support the robot's weight and the impact on the ground \cite{Zhong2019}.

@@

Quadruped robots move according to a gait pattern. The gait implemented for the robot follows the sequence of phases demonstrated in Fig. \ref{fig:trot_pattern}, in which the white rectangles represent the swing phase and the gray rectangles represent the stance phase. During the stance phase, the legs are on the ground and push the robot in the desired direction.  In the swing phase, the legs are raised and moved to the next support point. This gait pattern is called trot and is based on the concept of periodic and symmetrical gaits. The periodic gaits are characterized by the continuous repetition of the movements in the same instants. Symmetry is a characteristic of gaits that move a pair of legs together, leaving and returning to the ground in a synchronized way \cite{de2006quadrupedal}. Although the structure of the robot makes it possible to perform other types of gaits, in this work, only the trot was considered. To reduce the control complexity, a discontinuous gait was adopted, that is, the robot's body moves only when all the legs are on the ground, resulting in intermittent movement. In Fig. \ref{fig:trot_pattern}, it is noticeable that the same pair of diagonal legs always move at the same instant. Between two consecutive swing phases, there is a moment when all legs are in the stance phase, which is when the robot body is displaced in the desired direction of locomotion.

@@

The control subsystem of the robot is composed of two main components: the joints' controllers, and the body's stabilization controller. The joints' controllers, each one a PID, are responsible for controlling each joint of the robot independently. Meanwhile, the body's stabilization controller is responsible for controlling the pitch and roll angles of the robot \cite{Shi2021} \cite{Shi2021}\cite{StanfordQuadruped}, maintaining it at 0 degrees.

@@

\begin{thebibliography}{00}
  \bibitem{X.134} X. Zhang, L. Lang, J. Wang, and H. Ma, ‘The quadruped robot locomotion based on force control’, Proceedings of the 2015 27th Chinese Control and Decision Conference, CCDC 2015, pp. 5440–5445, 2015.
  \bibitem{ROS2Humble} S. Macenski, T. Foote, B. Gerkey, C. Lalancette, and W. Woodall, ‘Robot Operating System 2: Design, architecture, and uses in the wild’, Science Robotics, vol. 7, no. 66, p. eabm6074, 2022.
  \bibitem{Shi2021} Y. Shi, S. Li, M. Guo, Y. Yang, D. Xia, and X. Luo, ‘Structural design, simulation and experiment of quadruped robot’, Applied Sciences (Switzerland), vol. 11, 2021.
  \bibitem{leotti2005comparaccao} V. B. Leotti, A. R. Birck, and J. Riboldi, ‘Comparação dos Testes de Aderência à Normalidade Kolmogorov-smirnov, Anderson-Darling, Cramer--Von Mises e Shapiro-Wilk por Simulação’, Anais do 11\textordmasculine Simpósio de Estatística Aplicada à Experimentação Agronômica, 2005.
  \bibitem{cano2012six} E. L. Cano, J. M. Moguerza, and A. Redchuk, Six sigma with R: statistical engineering for process improvement, vol. 36. Springer Science \& Business Media, 2012.
  \bibitem{CaramelRepo} B. S. de Alencar, F. M. S. M. Barreto, and L. L. Souza (2022), ‘Caramel’, [Source Code]. https://github.com/Brazilian-Institute-of-Robotics/bir-black-mouth.
  \bibitem{Kitano2016} S. Kitano, S. Hirose, A. Horigome, and G. Endo, ‘TITAN-XIII: sprawling-type quadruped robot with ability of fast and energy-efficient walking’, ROBOMECH Journal, vol. 3, pp. 1–16, 2016.
  \bibitem{Zhong2019} Y. Zhong, R. Wang, H. Feng, and Y. Chen, ‘Analysis and research of quadruped robot’s legs: A comprehensive review’, International Journal of Advanced Robotic Systems, vol. 16, 3 2019.
  \bibitem{de2006quadrupedal} P. G. De Santos, E. Garcia, and J. Estremera, Quadrupedal locomotion: an introduction to the control of four-legged robots, vol. 1. Springer, 2006.
  \bibitem{StanfordQuadruped} N. Kau, A. Z. Schultz, and M. Bowers, Stanford Quadruped (2021), [Source Code]. https://github.com/stanfordroboticsclub/StanfordQuadruped.

  % 14   STANFORD Quadruped. Dispon ́ıvel em:〈https://github.com/stanfordroboticsclub/StanfordQuadruped〉. Acesso: 24 de nov de 2022.15   DIY hobby servos quadruped robot.Dispon ́ıvel em:〈https://hackaday.io/project/171456-diy-hobby-servos-quadruped-robot〉.Acesso: 24 de nov de 2022.
  % 15   DIY hobby servos quadruped robot.Dispon ́ıvel em:〈https://hackaday.io/project/171456-diy-hobby-servos-quadruped-robot〉.Acesso: 24 de nov de 2022.
  % 17   NOTSPOT robot simulation. Dispon ́ıvelem:〈https://github.com/lnotspotl/notspot_sim_cpp〉. Acesso: 24 de nov de 2022.

  % \bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
  % \bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
  % \bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
  % \bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
  % \bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
  % \bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
  % \bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
% \vspace{12pt}
% \color{red}
% IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.
